Fields COVID-19 dataset exploration

### 2023-01-11 data_cleaning/Data_cleaning_and_covariates_Jan_09.qmd
No missing obs. fixed model works

#write.csv(clean_data,here("data","clean_dataset.csv"),row.names = FALSE)
```

@@

@@

@@

>>>>

@@

#load health regions with missing entries fixed

@@

#rename columns
mhru <- mhru %>%
  rename(Geographic_area_title=Geographic.area.title)

clean_data<-clean_data %>%
  left_join(mhru, by = c("city")) %>%
   mutate(LHIN = coalesce(LHIN.x,LHIN.y)) %>%
  select(-c(LHIN.x,LHIN.y,Full_title.x,Geographic.area.y,Geographic_area_title.y))%>%
  mutate(Health_Region=
    case_when(LHIN=="Central"~ "Central",
              LHIN=="Central West"~"Central",
              LHIN=="Mississauga Halton"~"Central",
              LHIN=="North Simcoe Muskoka"~"Central",
              LHIN=="Central East"~"East",
              LHIN=="South East"~"East",
              LHIN=="Champlain"~"East",
              LHIN=="North East"~"North East",
              LHIN=="North West"~"North West",
              LHIN=="Toronto Central"~"Toronto",
              LHIN=="South West"~"West",
              LHIN=="Hamilton Niagara Haldimand Brant (Hnhb)"~"West",
              LHIN=="Waterloo Wellington"~"West",
              LHIN=="Erie St. Clair"~"West"
    ))%>%
  rename(Geographic_area=Geographic.area.x,Geographic_area_title=Geographic_area_title.x)

@@

write.csv(clean_data,here("data","clean_dataset.csv"),row.names = FALSE)
```
